Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-06-06 Manuscript/main.tex
Update main.tex

\subsection{Macroevolution: elaboration is a common route to divergence among species}
We tested the expectation, derived from adaptive radiation theory, that species divergence is biased along phylogenetic lines of least resistance by calculating species-specific measures of $elaboration_{species}$ and $innovation_{species}$.
If lines of least resistance are stable among species then we expect that species typically fall on, or close to, a conserved phylogenetic major axis of beak variation ($elaboration_{species}$) rather than away from the axis ($innovation_{species}$).
To assess this we projected the beak shape data for each species onto %@L_linear_algebra_stuff @L_beak_shape
the major axes of evolutionary rate matrices of their orders (see supplementary materials \ref{Fig:phylogeny_supplement} for projection onto the major axes of beak shape variation from the class-wide phylogenetic major axis of beak variation or their super-order’s phylogenetic major axis of beak variation).
We found typically higher values of $elaboration_{species}$ than $innovation_{species}$ (Fig. \ref{Fig:phylogeny}) %@L_rephrase_wefound
and strong clustering of both $elaboration_{species}$ and $innovation_{species}$ (median $elaboration_{species}$ for all orders = 0.114, 95\%CI = 0.004-0.485;  $elaboration_{species}$ Pagel's $\lambda$ = 0.888; median $innovation_{species}$ for all orders = 0.071, 95\%CI = 0.018-0.224); $innovation_{species}$ Pagel's $\lambda$ = 0.848).%@L_ei_species_values. 
% GT: TODO: add code for reproducibility

>>>>

\subsection{Macroevolution: elaboration is a common route to divergence among species}
We tested the expectation, derived from adaptive radiation theory \cite{schluter1996adaptive,mcglothlin2018adaptive,slater2019hierarchy} %@L_cite_adaptive
, that species divergence is biased along phylogenetic lines of least resistance by calculating species-specific measures of $elaboration_{species}$ and $innovation_{species}$.
If lines of least resistance are stable among species then we expect that species typically fall on, or close to, a conserved phylogenetic major axis of beak variation ($elaboration_{species}$) rather than away from the axis ($innovation_{species}$).
To assess this we projected the beak shape data for each species onto %@L_linear_algebra_stuff @L_beak_shape
the major axes of evolutionary rate matrices of their orders (see supplementary materials \ref{Fig:phylogeny_supplement} for projection onto the major axes of beak shape variation from the class-wide phylogenetic major axis of beak variation or their super-order’s phylogenetic major axis of beak variation).
We found typically higher values of $elaboration_{species}$ than $innovation_{species}$ (Fig. \ref{Fig:phylogeny}) %@L_rephrase_wefound
and strong clustering of both $elaboration_{species}$ and $innovation_{species}$ (median $elaboration_{species}$ for all orders = 0.114, 95\%CI = 0.004-0.485;  $elaboration_{species}$ Pagel's $\lambda$ = 0.888; median $innovation_{species}$ for all orders = 0.071, 95\%CI = 0.018-0.224); $innovation_{species}$ Pagel's $\lambda$ = 0.848).%@L_ei_species_values. 
% GT: TODO: add code for reproducibility
